---
title: "Datacamp_Visualizing Big Data with Trelliscope__ggplot2 + TrelliscopeJS"
author: "dizhen"
date: "2019Äê4ÔÂ29ÈÕ"
output: html_document
---
# Trelliscope faceting gapminder by country
With a subset of the gapminder data (just the two countries in Oceania), take the example of life expectancy vs. year faceted by country and continent and create a TrelliscopeJS display.

The gapminder data set is available for you in your workspace.

Instructions 1/2

Plot a line showing life expectancy (lifeExp) on the y-axis vs. year on the x-axis using the proper geom_().
Use facet_trelliscope() to facet on country and continent. Note that to facet on two variables, the syntax is ~ var1 + var2

```{r}
library(ggplot2)
library(trelliscopejs)

# Create the plot
ggplot(gapminder, aes(x = year, y = lifeExp)) +
  geom_line() +
  # Facet on country and continent
  facet_trelliscope(~ country + continent)
```

Instructions 2/2

Set the name to "lifeExp_by_country" and desc to "Life expectancy vs. year per country".
Set the initial layout to show 1 row and 2 columns.
Note: Trelliscope displays are best viewed by expanding the HTML Viewer.

```{r}
library(ggplot2)
library(trelliscopejs)

ggplot(gapminder, aes(year, lifeExp)) +
  geom_line() +
  facet_trelliscope(~ country + continent,
    name = "lifeExp_by_country",
    desc = "Life expectancy vs. year per country",
    nrow = 1, ncol = 2
  )
```

# Customizing the gapminder display
Let's put some of these features to the test with our by-country life expectancy trajectory plot. Note that we are again working with just the two countries from Oceania.

Instructions

Add a geom_smooth() layer to add a fitted linear model using the "lm" method.
Set the scales to be "sliced".
With the linear model layer added to the plot, specify that automatic cognostics should be computed for this display and explore what new cognostics this layer adds to the display.

```{r}
library(trelliscopejs)
library(ggplot2)

# Create the plot
ggplot(gapminder, aes(year, lifeExp)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) +
  facet_trelliscope(~ country + continent,
    name = "lifeExp_by_country",
    desc = "Life expectancy vs. year for 142 countries.",
    nrow = 1, ncol = 2,
    # Set the scales
    scales = "sliced",
    # Specify automatic cognistics
    auto_cog = TRUE)
```

# Adding custom cognostics
Let's create some custom cognostics. To do so, you'll add two new variables to the gapminder data: delta_lifeExp and ihme_link.

Instructions

Add a new variable called delta_lifeExp to the gapminder data that computes the difference between the first and last observed life expectancy (lifeExp) for each country. Note that the data is already sorted by year.
Add another variable, ihme_link that links to the country's profile on healthdata.org, using space_to_dash() to replace spaces in country values to dashes. For example, for the country "Costa Rica", the link is "http://www.healthdata.org/Costa-Rica".
Give the delta_lifeExp variable a description of "Overall change in life expectancy".
Specify default_label = TRUE to make the ihme_link variable be shown as a label by default.

```{r}
library(ggplot2)
library(dplyr)
library(gapminder)
library(trelliscopejs)
space_to_dash <- function(x) gsub(" ", "-", x)

# Group by country and create the two new variables
gap <- gapminder %>%
  group_by(country) %>%
  mutate(
    delta_lifeExp = tail(lifeExp, 1) - head(lifeExp, 1),
    ihme_link = paste0("http://www.healthdata.org/", space_to_dash(country)))

# Add the description
gap$delta_lifeExp <- cog(gap$delta_lifeExp, desc = "Overall change in life expectancy")
# Specify the default label
gap$ihme_link <- cog(gap$ihme_link, default_label = TRUE)

ggplot(gap, aes(year, lifeExp)) +
  geom_point() +
  facet_trelliscope(~ country + continent,
    name = "lifeExp_by_country",
    desc = "Life expectancy vs. year.",
    nrow = 1, ncol = 2,
    scales = c("same", "sliced"))
```

